### 2018-01-04 Simulator/article.tex
la2pdf commit - 2018:01:04	11:27:54	(to. 4.jan.)

\newcommand\graphicsAI[2][]{%
  \immediate\write18{./bin/laFigure #2 #1}%
  \input{result}}%

@@

\begin{figure*}[t]\centering%
\graphicsAI[width=\linewidth]{gfx/scene_coordinate_system.svg}%
\caption{Simulator principle. A model of the seafloor and object is first loaded into OpenGL, and an orthogonal camera view set up to match the desired image region on the seafloor. Then the scene is rendered and an intensity image and a depth map is created. The intensity image along with the depth information is finally combined to form a sonar like image. This is our template.}\label{simulator_coordinate_system}%
\end{figure*}

\begin{figure*}[t]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/simulator.svg}%
\caption{Simulator concept.}\label{buildup}%
\end{figure*}

@@

The mapping of the vertices from object coordinates to image coordinates happen through a set of transformations:
%
\begin{align*}
\bmat{x\\y\\0\\1}_\text{image} = \P \cdot \V \cdot \M \cdot \bmat{x\\y\\z\\1}_\text{object},
\end{align*}
%
where $\bmat{\cdot}_\text{model}$ is the loaded model, $\bmat{\cdot}_\text{image}$ is the output image, and $\M$, $\V$ and $\P$ are transformation matrices. These will be described next.

The first transform we apply is the model matrix $\M$, which operates in the model's local coordinate system. It is defined as
%
\begin{align}
\M = \bmat{x_t \\ y_t \\ z_t \\ w}_\text{\parbox{1cm}{\setlength\baselineskip{0.3cm}transformed\\model}} &= \boldsymbol{T} \cdot \R \cdot \boldsymbol{S} \bmat{x \\ y \\ z \\ w}_\text{model},
\end{align}
%
where $\boldsymbol{S}, \R$ and $\boldsymbol{T}$ are matrices\todo{be explicit on dependencies?} for scaling, rotation and translation, respectively. These are provided for reference in Appendix \ref{transformation_matrices}.

@@

\begin{figure}[t]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/opengl_part.svg}%
\caption{Setting camera top and bottom boundaries.}\label{camera_top_bottom}%
\end{figure}

@@

\begin{figure*}[!tbp]\centering%
\graphicsAI[width=\linewidth]{gfx/fig_images_sonar_simulator_tagged.svg}\label{fig_images_sonar_simulation}%
\caption{Selected objects. Top row show SAS images of 2 cylinders and a torpedo located in the Jesus Bay, Norway. Center row show the best match from a conventional template matcher, and bottom row show the adaptive template matcher. The contour of the SAS object is indicated with red lines. Note that the adaptive technique produce templates with a better fit to the highlight, but that this does not necessarily lead to a better match against the shadow.}
\end{figure*}

\begin{figure*}[!tbp]\centering%
\graphicsAI[width=\linewidth]{gfx/fig_rocs.pdf}\label{fig_roc_curves}%
\caption{Receiver operating characteristics (ROC) curves.}
\end{figure*}

\begin{figure*}[!tbp]\centering%
\graphicsAI[width=\linewidth]{gfx/fig_overlay.pdf}%
% \parbox{\linewidth}{\small\centering\vspace{.5\baselineskip}
% \newline\centering\newline %\\[.5\baselineskip]
\newcommand\cdesc[2]{{\raggedright\setlength\fboxsep{0pt}
\fbox{\colorbox[HTML]{#1}{\vrule height8.5pt depth3.5pt width0pt\hspace{.5cm}}}\ \ #2\\}}
\begin{minipage}{.4\linewidth}
\cdesc{800000}{Template highlight and image highlight}
\cdesc{FF1000}{Template highlight only}
\cdesc{FFEB00}{Image highlight only}
\cdesc{83FF7C}{Background pixels}
\end{minipage}%
\begin{minipage}{.4\linewidth}
\cdesc{000083}{Template shadow and image shadow}
\cdesc{0014FF}{Template shadow only}
\cdesc{00EFFF}{Image shadow only}
\cdesc{00A7FF}{Template shadow and image highlight}
\end{minipage}%}
\caption{Comparison of classification performance for the standard and adaptive template technique. The three objects were more or less arbitrary picked from the scene. For the roughly 3\,m long cylinders both methods perform similarly, the standard method seemingly with a slight edge. This is no surprise given that the 3\,m long cylinder model that make up the static template database fit the actual object well here. However, for the longer torpedo-like object the adaptive technique is clearly better. This is its merit; for objects and geometries that are not included in the static template database we can expect the adaptive techniques to perform better.}\label{fig_image_simulation}%
\end{figure*}

@@

% \begin{figure*}[!tbp]\centering%
% \subfloat[SAS images of 2 cylinders and a torpedo.]{%
% \graphicsAI[width=0.5\linewidth]{gfx/fig_images_sonar_simulation.pdf}%
% \label{fig_sonar_simulation}}%
% \subfloat[Cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.]{
% \graphicsAI[drawing,width=0.5\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
% \label{sim_cylinder}}%
% \caption{A SAS image of a cylinder and a template simulation adapted to it.}
% \end{figure*}
% 
% 
% \begin{figure*}[!tbp]\centering%
% \subfloat[SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.]{%
% \graphicsAI[drawing,width=0.5\linewidth]{gfx/data_cylinder_submerged.svg}%
% \label{data_cylinder}}%
% \subfloat[Cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.]{
% \graphicsAI[drawing,width=0.5\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
% \label{sim_cylinder}}%
% \caption{A SAS image of a cylinder and a template simulation adapted to it.}
% \end{figure*}

>>>>

\let\oldincludegraphics\includegraphics
\renewcommand\includegraphics[2][]{%
  \immediate\write18{./bin/laFigure #2 #1}%
  \input{result}}%

@@

\begin{figure*}[t]\centering%
\includegraphics[width=\linewidth]{gfx/scene_coordinate_system.svg}%
\caption{Simulator principle. A model of the seafloor and object is first loaded into OpenGL, and an orthogonal camera view set up to match the desired image region on the seafloor. Then the scene is rendered and an intensity image and a depth map is created. The intensity image along with the depth information is finally combined to form a sonar like image. This is our template.}\label{simulator_coordinate_system}%
\end{figure*}

\begin{figure*}[t]\centering%
\includegraphics[drawing,width=\linewidth]{gfx/simulator.svg}%
\caption{Simulator concept.}\label{buildup}%
\end{figure*}

@@

The mapping of the vertices from object coordinates to image coordinates happen through a set of transformations:
%
\begin{align*}
\bmat{x\\y\\0\\1}_\text{image} = \boldsymbol{P} \cdot \boldsymbol{V} \cdot \boldsymbol{M} \cdot \bmat{x\\y\\z\\1}_\text{object},
\end{align*}
%
where $\bmat{\cdot}_\text{model}$ is the loaded model, $\bmat{\cdot}_\text{image}$ is the output image, and $\M$, $\V$ and $\P$ are transformation matrices. These will be described next.

The first transform we apply is the model matrix $\M$, which operates in the model's local coordinate system. It is defined as
%
\begin{align}
\M = \bmat{x_t \\ y_t \\ z_t \\ w}_\text{\parbox{1cm}{\setlength\baselineskip{0.3cm}transformed\\model}} &= \boldsymbol{T} \cdot \boldsymbol{R} \cdot \boldsymbol{S} \bmat{x \\ y \\ z \\ w}_\text{model},
\end{align}
%
where $\boldsymbol{S}$, $\boldsymbol{R}$ and $\boldsymbol{T}$ are matrices\todo{be explicit on dependencies?} for scaling, rotation and translation, respectively. These are provided for reference in Appendix \ref{transformation_matrices}.

@@

\begin{figure}[t]\centering%
\includegraphics[drawing,width=\linewidth]{gfx/opengl_part.svg}%
\caption{Setting camera top and bottom boundaries.}\label{camera_top_bottom}%
\end{figure}

@@

\begin{figure*}[!tbp]\centering%
\includegraphics[width=\linewidth]{gfx/fig_images_sonar_simulator_tagged.svg}\label{fig_images_sonar_simulation}%
\caption{Selected objects. Top row show SAS images of 2 cylinders and a torpedo located in the Jesus Bay, Norway. Center row show the best match from a conventional template matcher, and bottom row show the adaptive template matcher. The contour of the SAS object is indicated with red lines. Note that the adaptive technique produce templates with a better fit to the highlight, but that this does not necessarily lead to a better match against the shadow.}
\end{figure*}

\begin{figure*}[!tbp]\centering%
\includegraphics[width=\linewidth]{gfx/fig_rocs.pdf}\label{fig_roc_curves}%
\caption{Receiver operating characteristics (ROC) curves.}
\end{figure*}

\begin{figure*}[!tbp]\centering%
\includegraphics[width=\linewidth]{gfx/fig_overlay.pdf}%
% \parbox{\linewidth}{\small\centering\vspace{.5\baselineskip}
% \newline\centering\newline %\\[.5\baselineskip]
\newcommand\cdesc[2]{{\raggedright\setlength\fboxsep{0pt}
\fbox{\colorbox[HTML]{#1}{\vrule height8.5pt depth3.5pt width0pt\hspace{.5cm}}}\ \ #2\\}}
\begin{minipage}{.4\linewidth}
\cdesc{800000}{Template highlight and image highlight}
\cdesc{FF1000}{Template highlight only}
\cdesc{FFEB00}{Image highlight only}
\cdesc{83FF7C}{Background pixels}
\end{minipage}%
\begin{minipage}{.4\linewidth}
\cdesc{000083}{Template shadow and image shadow}
\cdesc{0014FF}{Template shadow only}
\cdesc{00EFFF}{Image shadow only}
\cdesc{00A7FF}{Template shadow and image highlight}
\end{minipage}%}
\caption{Comparison of classification performance for the standard and adaptive template technique. The three objects were more or less arbitrary picked from the scene. For the roughly 3\,m long cylinders both methods perform similarly, the standard method seemingly with a slight edge. This is no surprise given that the 3\,m long cylinder model that make up the static template database fit the actual object well here. However, for the longer torpedo-like object the adaptive technique is clearly better. This is its merit; for objects and geometries that are not included in the static template database we can expect the adaptive techniques to perform better.}\label{fig_image_simulation}%
\end{figure*}

@@

% \begin{figure*}[!tbp]\centering%
% \subfloat[SAS images of 2 cylinders and a torpedo.]{%
% \includegraphics[width=0.5\linewidth]{gfx/fig_images_sonar_simulation.pdf}%
% \label{fig_sonar_simulation}}%
% \subfloat[Cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.]{
% \includegraphics[drawing,width=0.5\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
% \label{sim_cylinder}}%
% \caption{A SAS image of a cylinder and a template simulation adapted to it.}
% \end{figure*}
% 
% 
% \begin{figure*}[!tbp]\centering%
% \subfloat[SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.]{%
% \includegraphics[drawing,width=0.5\linewidth]{gfx/data_cylinder_submerged.svg}%
% \label{data_cylinder}}%
% \subfloat[Cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.]{
% \includegraphics[drawing,width=0.5\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
% \label{sim_cylinder}}%
% \caption{A SAS image of a cylinder and a template simulation adapted to it.}
% \end{figure*}

### 2018-01-04 ThesisJo/introduction.tex
la2pdf commit - 2018:01:04	11:27:54	(to. 4.jan.)

Preface
  Way too complex a topic to be covered in fully detail. Perhaps impossible?
  Interesting enough to be covered, even if just partially.
  Complexity issue - picture from essay

Introduction
   A marvel of science, the world, and beyond
      Intelligence / conscience. What is it?
      HPC bridging learning and big data
   Machine intelligence / adaptivity / Deep learning
      Means for intelligence?
      Adapts to data
      Proven powerful
      Hard to understand, hard to control
      Data hungry
      Fascinating perspectives:
      - Local dependencies work on e.g. images. Due to lack of data?
      - First layer similar to template matching (convolitional network)
      - If we can't understand it, perhaps we can parent it? Society's norms a giant assemble of prior knowledge.
      - Deep neural nets interconnected, learning from each other?
      - The brain adapts its wiring to solve tasks, does this carry over?
      - Neuman networks - recursive
   Big data
      Fundament of intelligence?
      Amount of data recorded and stored immense. Sensors everywhere.
      Phones, internet searches, smart watches, cars, surveillance cams,   
   High performance computing
      Engine of intelligence?
      Combining deep learning with big data
      Improving at a rapid pace

>>>>

Preface
  Way too complex a topic to be covered in fully detail. Perhaps impossible?
  Interesting enough to be covered, even if just partially.
  Complexity issue - picture from essay.
     - We observe the world from one location. The internet lets machine see everything.
     - Mental constraint. Can machines break through it?

Introduction
   A marvel of science, the world, and beyond
      Intelligence / conscience. What is it?
      HPC bridging learning and big data
      Deep Patient, Google Brain, Nvidia self driving cars, Bloomberg money machine, image and speech analysis, ...
   Information processing
      Instrinsic and extrinsic information
      Data decomposition
      Data volume
      Amount of information, rank, dimensions

   Machine intelligence / adaptivity / Deep learning
      Means for intelligence?
      Adapts to data
      Proven powerful
      Hard to understand, hard to control
      Data hungry
      Fascinating perspectives:
      - Local dependencies work on e.g. images. Due to lack of data?
      - First layer similar to template matching (convolitional network)
      - If we can't understand it, perhaps we can parent it? Society's norms a giant assemble of prior knowledge.
      - Deep neural nets interconnected, learning from each other?
      - The brain adapts its wiring to solve tasks, does this carry over?
      - Neuman networks - recursive
      - Energy efficient. But the body does it MUCH better
      - Only make the choices that are relevant. Adaptivity vs. computational/data requirements
        - The body has a lot of information stored in the genome. It doesn't start from scratch
      - On images - convolutional networks
        - Layers offer image feature representation of different scales (intuition: create extrinsic shift invariance)
   Big data
      Fundament of intelligence?
      Amount of data recorded and stored immense. Sensors everywhere.
      Phones, internet searches, smart watches, cars, surveillance cams,   
   High performance computing
      Engine of intelligence?
      Combining deep learning with big data
      Improving at a rapid pace
      Quantum computers seem very adapt at deep learning, with node-like structure
      FPGA might fill a gap too. Hardware generated adaptively. Efficient information exchange often more effective than processing power. Current architectures limited by bandwidth for most applications.
